
\begin{thebibliography}{1}

\bibitem{giraud}
Giraud, C. (2005). DFA on AES. In: Dobbertin, H., Rijmen, V., Sowa, A. (eds) Advanced Encryption Standard – AES. AES 2004. Lecture Notes in Computer Science, vol 3373. Springer, Berlin, Heidelberg. https://doi.org/10.1007/11506447\_4

\bibitem{optical}
Skorobogatov, S.P., Anderson, R.J. (2003). Optical Fault Induction Attacks. In: Kaliski, B.S., Koç, ç.K., Paar, C. (eds) Cryptographic Hardware and Embedded Systems - CHES 2002. CHES 2002. Lecture Notes in Computer Science, vol 2523. Springer, Berlin, Heidelberg. https://doi.org/10.1007/3-540-36400-5\_2

\bibitem{pmaurine2012}
Philippe Maurine, Karim Tobich, Thomas Ordas, Pierre yvan Liardet. Yet Another Fault Injection Technique : by Forward Body Biasing Injection. YACC'2012: Yet Another Conference on Cryptography, Sep 2012, Porquerolles Island, France. (lirmm-00762035)

\bibitem{ktobich2013}
K. Tobich, P. Maurine, P. -. Liardet, M. Lisart and T. Ordas, "Voltage Spikes on the Substrate to Obtain Timing Faults," 2013 Euromicro Conference on Digital System Design, 2013, pp. 483-486, doi: 10.1109/DSD.2013.146.

\bibitem{nbb2016}
Noemie Beringuier-Boher, Marc Lacruche, David El-Baze, Jean-Max Dutertre, Jean-Baptiste Rigaud, et al.. Body Biasing Injection Attacks in Practice . CS2: Cryptography and Security in Computing Systems, Jan 2016, Prague, Czech Republic. pp.49-54, (10.1145/2858930.2858940). (lirmm-0143414)

\bibitem{oflynn2020}
Colin O'Flynn.
\newblock Low-cost body biasing injection {(BBI)} attacks on {WLCSP} devices.
\newblock In Pierre{-}Yvan Liardet and Nele Mentens, editors, {\em{CARDIS}
2020, Virtual Event, November 18-19, 2020, Revised Selected Papers}, volume
12609 of {\em Lecture Notes in Computer Science}, pages 166--180. Springer,
2020.

\bibitem{mathieuEMFI}
M. Dumont, M. Lisart and P. Maurine, "Modeling and Simulating Electromagnetic Fault Injection," in IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems, vol. 40, no. 4, pp. 680-693, April 2021, doi: 10.1109/TCAD.2020.3003287.

\bibitem{lfitriplewell}
Nicolas Borrel, Clément Champeix, Edith Kussener, Wenceslas Rahajandraibe, Mathieu Lisart, et al.. Influence of triple-well technology on laser fault injection and laser sensor efficiency. IEEE International Symposium on Defect and Fault Tolerance in VLSI and Nanotechnology Systems (DFTS 2015), Oct 2015, Amherst, MA, United States. (10.1109/DFT.2015.7315141). (emse-01227366)

\bibitem{techEM}
P. Maurine, "Techniques for EM Fault Injection: Equipments and Experimental Results," 2012 Workshop on Fault Diagnosis and Tolerance in Cryptography, 2012, pp. 3-4, doi: 10.1109/FDTC.2012.21.

\bibitem{phototriple}
Nicolas Borrel, Clément Champeix, Mathieu Lisart, Alexandre Sarafianos, Edith Kussener, et al.. Characterization and simulation of a body biased structure in triple-well technology under pulsed photoelectric laser stimulation. International Symposium for Testing and Failure Analysis (ISTFA), Nov 2014, Houston, United States. (emse-01099035)

\bibitem{mybbi1}
Chancel, G., Galliere, J.-M., Maurine, P. (2022). Body Biasing Injection: To Thin or Not to Thin the Substrate?. In: Balasch, J., O’Flynn, C. (eds) Constructive Side-Channel Analysis and Secure Design. COSADE 2022. Lecture Notes in Computer Science, vol 13211. Springer, Cham. https://doi.org/10.1007/978-3-030-99766-3\_6.

\bibitem{mybbi2}
G. Chancel, J.-M. Galliere and P. Maurine, "Body Biasing Injection: Impact of substrate types on the induced disturbances," 2022 Workshop on Fault Detection and Tolerance in Cryptography (FDTC), Italy, 2022, pp. 50-60, doi: 10.1109/FDTC57191.2022.00015.

\bibitem{japBBI}
T. Wadatsumi et al., "Voltage Surges by Backside ESD Impacts on IC Chip in Flip Chip Packaging," 2022 IEEE International Reliability Physics Symposium (IRPS), 2022, pp. P14-1-P14-6, doi: 10.1109/IRPS48227.2022.9764457.

\bibitem{piretQuis}
Christophe Giraud and Adrian Thillard. Piret and Quisquater's DFA on AES Revisited. Cryptology ePrint Archive, Paper 2010/440, 2010.

\bibitem{powerGlitch}
L. Zussa, J. -M. Dutertre, J. Clédière and A. Tria, "Power supply glitch induced faults on FPGA: An in-depth analysis of the injection mechanism," 2013 IEEE 19th International On-Line Testing Symposium (IOLTS), Chania, Greece, 2013, pp. 110-115, doi: 10.1109/IOLTS.2013.6604060.

\end{thebibliography}
